Hydrogen Epoch of Reionization Array (HERA)

### 2016-04-07 manuscript.tex
update to sensitivity figure

Since the thermal noise per visibility baseline may be expressed as
\begin{equation}
V_N = \left(\frac{2k_B}{\lambda^2}\right)\left(\frac{T_{sys}}{\sqrt{2B\tau}}\right)\Omega_b B
\label{eq:sensitivity_per_baseline}
\end{equation}
where $\tau$ is the integration time (see {\em e.g.} TMS),
to determine the sensitivity of an instrument to the power spectrum per baseline we can substitute the thermal noise per baseline for the visibility in Eq. \ref{eq:Pk_baseline}.  Further, since an interferometer typically measures many baselines which may be averaged together to improve the signal-to-noise per $k$-bin, the total sensitivity may be approximated as
\begin{equation}
\Delta^2_N (k,z)\approx \frac{k^3X^2(z)Y(z)}{4\pi^2} \left[\frac{T_{sys}^2(z)\Omega_b(z) }{\tau(z) \mathcal{N}_s(k)}\right]
\label{eq:sensitivity}
\end{equation}
where $\mathcal{N}$ represents the improvement in sensitivity based on the array configuration, which may significantly boost the sensitivity if optimized for this measurement 
(see \cite{parsons_et_al2012b}).  Fig. \ref{fig:boost} plots this ``boost'' factor for various telescopes under nominal observing campaigns using the delay-spectrum technique.  The large improvement for PAPER and HERA is the fact that the baselines are redundantly placed on appropriate spatial scales, so that a more limited number of unique baselines get sampled many times.

\begin{figure}[h!]
\centerline{
\includegraphics[width=0.5\textwidth]{plots/boost.png}
}
\caption{Representative boost factors ($\mathcal{N}$ in Eq. \ref{eq:sensitivity}) for representative observing campaigns for various instruments.
ADD NEW HERA CONFIGURATION AND LOFAR AND PUT IN 'HOW TO MAKE THIS PLOT'}
\label{fig:boost}
\end{figure}

>>>>

Since the thermal noise per visibility baseline may be expressed as
\begin{equation}
V_N = \left(\frac{2k_B}{\lambda^2}\right)\left(\frac{T_{sys}}{\sqrt{2B\tau}}\right)\Omega_b B
\label{eq:sensitivity_per_baseline}
\end{equation}
where $\tau$ is the integration time (see {\em e.g.} TMS),
to determine the sensitivity of an instrument to the power spectrum per baseline we can substitute the thermal noise per baseline for the visibility in Eq. \ref{eq:Pk_baseline}.  Further, since an interferometer typically measures many baselines which may be averaged together to improve the signal-to-noise per $k$-bin, the total sensitivity may be approximated as
\begin{equation}
\Delta^2_N (k,z)\approx \frac{k^3X^2(z)Y(z)}{4\pi^2} \left[\frac{T_{sys}^2(z)\Omega_b(z) }{\tau(z) \mathcal{N}_s(k)}\right]
\label{eq:sensitivity}
\end{equation}
where $\mathcal{N}$ represents the improvement in sensitivity based on the array configuration, which may significantly boost the sensitivity if optimized for this measurement 
(see \cite{parsons_et_al2012b}).  Fig. \ref{fig:boost} plots this ``boost'' factor for various configuration types relative to an array in a 19-element hexagonal configuration.  They are labelled for the type of configuration (hex, grid, imaging) and the number of antennas (from 37 to 350).  Note that the hex is based on the configuration used for HERA, grid for that of PAPER, Imaging-128 for MWA and Imaging-48 for LOFAR.  The plot shows that for a fixed number using the delay-spectrum approach, redundant arrays (hex/grid) provide about an order of magnitude improvement over imaging arrays.  Since the baselines go as order $N^2$, that corresponds to that for about 1/3 the number of elements you get the same performance (as verified by the Hex-37/Imaging-128 lines).  This advantage does not extend to the other approaches discussed below.

Another approach to improving sensitivity is to make the collecting area per element larger.

\begin{figure}[h!]
\centerline{
\includegraphics[width=0.5\textwidth]{plots/boost.pdf}
\includegraphics[width=0.5\textwidth]{plots/sensratio.pdf}
}
\caption{Left: Representative boost factors ($\mathcal{N}$ in Eq. \ref{eq:sensitivity}) normalized to a 19-element hexagonal configuration spaced at 14.6m.  For a given element count, one can get about an order of
magnitude improvement in delay-spectrum sensitivity.  Alternatively, for the same sensitivity one can build roughly 1/3 the antennas.  Right:  Power spectrum sensitivities for various arrays normalized to the
19-element hex.  Here the element size is included, which is shown as an appropriately sized circle.}
\label{fig:boost}
\end{figure}
